Web-based Supplementary Materials for A Space-time Skew-$t$ Model for Threshold Exceedances by Morris, Reich, Thibaud, and Cooley

### 2016-06-18 LaTeX/supplemental_rev.tex
manuscript and plot updates

\subsection*{Spatial knot locations}
For each day, we update the spatial knot locations, $\bw_1, \ldots, \bw_K$, using a Metropolis-Hastings block update.
Because the spatial domain is bounded, we generate candidate knots using the transformed knots $\bw^*_1, \ldots, \bw^*_K$ (see \sref{sts:temporal}) and a random walk bivariate Gaussian candidate distribution
\begin{align*}
	{\bw^*_k}^{(c)} \sim \text{N}({\bw^*_k}^{(r - 1)}, s^2 I_2)
\end{align*}
where ${\bw^*_k}^{(r - 1)}$ is the location for the transformed knot at MCMC iteration $r - 1$, $s$ is a tuning parameter, and $I_2$ is an identity matrix.
After candidates have been generated for all $K$ knots, the acceptance ratio is
\begin{align*}
  R = \left\{ \frac{ l[ Y_t(\bs | \bw_1^{(c)}, \ldots, \bw_K^{(c)}, \ldots)] }{l[ Y_t(\bs | \bw_1^{(r - 1)}, \ldots, \bw_K^{(r - 1)}, \ldots)]} \right\} \times \left\{ \frac{ \prod_{k = 1}^{K}\phi(\bw_k^{(c)})}{ \prod_{k = 1}^{K}\phi(\bw_k^{(r - 1)})} \right\} \times \left\{ \frac{ \prod_{k = 1}^{K} p({\bw^*_k}^{(c)})}{ \prod_{k = 1}^{K} p({\bw^*_k}^{(r - 1)})}\right\}
\end{align*}
where $l$ is the likelihood given in \eref{steq:hier}, and $p(\cdot)$ is the prior either taken from the time series given in \eref{sts:temporal} or assumed to be uniform over $\calD$.
The candidate knots are accepted with probability $\min\{R, 1\}$.

\subsection*{Spatial random effects}
If there is no temporal dependence amongst the observations, we use a Gibbs update for $z_{tk}$, and the posterior distribution is given in \aref{sta:posterior}.
If there is temporal dependence amongst the observations, then we update $z_{tk}$ using a Metropolis-Hastings update.
Because this model uses $|z_{tk}|$, we generate candidate random effects using the $z^*_{tk}$ (see \sref{sts:temporal}) and a random walk Gaussian candidate distribution
\begin{align*}
  {z^*_{tk}}^{(c)} \sim \text{N}({z^*_{tk}}^{(r - 1)}, s^2)
\end{align*}
where ${z^*_{tk}}^{(r-1)}$ is the value at MCMC iteration $r - 1$, and $s$ is a tuning parameter.
The acceptance ratio is
\begin{align*}
  R = \left\{ \frac{ l[Y_t(\bs) | z_{tk}^{(c)}, \ldots] }{ l[Y_t(\bs) | z_{tk}^{(r - 1)}]} \right\} \times \left\{ \frac{ p[ z_{tk}^{(c)} ] }{ p[ z_{tk}^{(r - 1)}]}\right\}
\end{align*}
where $p[\cdot]$ is the prior taken from the time series given in \sref{sts:temporal}.
The candidate is accepted with probability $\min\{R, 1\}$.

\subsection*{Variance terms}
When there is more than one site in a partition, then we update $\sigma^2_{tk}$ using a Metropolis-Hastings update.
First, we generate a candidate for $\sigma^2_{tk}$ using an IG$(a^*/s, b^*/s)$ candidate distribution in an independence Metropolis-Hastings update where $a^* = (n_{tk} + 1) / 2 + a$, $b^* = [Y_{tk}^\prime \Sigma^{-1}_{tk} Y_{tk} + z_{tk}^2] / 2 + b$, $n_{tk}$ is the number of sites in partition $k$ on day $t$, and $Y_{tk}$ and $\Sigma^{-1}_{tk}$ are the observations and precision matrix for partition $k$ on day $t$.
The acceptance ratio is
\begin{align*}
  R = \left\{
    \frac{ l[Y_t(\bs) | {\sigma^2_{tk}}^{(c)}, \ldots] }
         { l[Y_t(\bs) | {\sigma^2_{tk}}^{(r - 1)}]}
    \right\} \times \left\{
    \frac{ l[z_{tk} | {\sigma^2_{tk}}^{(c)}, \ldots] }
         { l[z_{tk} | {\sigma^2_{tk}}^{(r - 1)}, \ldots] }
    \right\} \times \left\{
    \frac{ p[ {\sigma^2_{tk}}^{(c)} ] }
         { p[ {\sigma^2_{tk}}^{(r - 1)}] }
    \right\} \times \left\{
    \frac{ c[ {\sigma^2_{tk}}^{(r - 1)}] }
         { c[ {\sigma^2_{tk}}^{(c)}]}
    \right\}
\end{align*}
where $p[\cdot]$ is the prior either taken from the time series given in \sref{sts:temporal} or assumed to be IG$(a, b)$, and $c[\cdot]$ is the candidate distribution.
The candidate is accepted with probability $\min\{R, 1\}$.

\subsection*{Spatial covariance parameters}
We update the three spatial covariance parameters, $\log(\rho)$, $\log(\nu)$, $\gamma$, using a Metropolis-Hastings block update step.
First, we generate a candidate using a random walk Gaussian candidate distribution
\begin{align*}
	\log(\rho)^{(c)} \sim \text{N}(\log(\rho)^{(r - 1)}, s^2)
\end{align*}
where $\log(\rho)^{(r-1)}$ is the value at MCMC iteration $r - 1$, and $s$ is a tuning parameter.
Candidates are generated for $\log(\nu)$ and $\gamma$ in a similar fashion.
The acceptance ratio is
\begin{align*}
	R = \left\{ \frac{ \prod_{t = 1}^{T} l[Y_t(\bs) | \rho^{(c)}, \nu^{(c)}, \gamma^{(c)}, \ldots] }{\prod_{t = 1}^{T} l[Y_t(\bs) | \rho^{(r-1)}, \nu^{(r-1)}, \gamma^{(r-1)}, \ldots] } \right\} \times \left\{ \frac{ p[\rho^{(c)}] }{ p[\rho^{(r - 1)] } } \right\} \times \left\{ \frac{ p[\nu^{(c)}] }{ p[\nu^{(r - 1)}] } \right\} \times \left\{ \frac{ p[ \gamma^{(c)} ] }{ p[\gamma^{(r - 1)} ] } \right\}.
\end{align*}
All three candidates are accepted with probability $\min\{R, 1\}$.

@@

\subsection*{Conditional posterior of $z_{tk} \mid \ldots $}\label{sts:mvcondu}
If knots are independent over days, then the conditional posterior distribution of $|z_{tk}|$ is conjugate.
For simplicity, drop the subscript $t$, let $\tilde{z}_{tk} = |z_{tk}|$, and define
\begin{align*}
R(\bs) = \left\{
    \begin{array}{ll}
        Y(\bs) - X(\bs) \beta &s \in P_l\\[1em]
        Y(\bs) - X(\bs) \beta - \lambda \tilde{z}(\bs) \qquad & s \notin P_l
    \end{array}
\right.
\end{align*}
Let
\begin{align*}
    R_1 &= \text{the vector of } R(\bs) \text{ for } s \in P_l \\
    R_2 &= \text{the vector of } R(\bs) \text{ for } s \notin P_l \\
    \Omega &= \Sigma^{-1}.
\end{align*}
Then
\begin{align*}
    \pi(z_l | \ldots) &\propto \exp \left\{ -\frac{ 1 }{ 2 } \left[
        \left( \begin{array}{c}
            R_1 - \lambda \tilde{z}_l \bOne\\
            R_2
        \end{array} \right)^\prime
        \left( \begin{array}{cc}
            \Omega_{11} & \Omega_{12}\\
            \Omega_{21} & \Omega_{22}
        \end{array} \right)
        \left( \begin{array}{c}
            R_1 - \lambda \tilde{z}_l \bOne\\
            R_2
        \end{array} \right)
        +  \frac{ {\tilde{z}_l}^2 }{ \sigma_l^2 }\right]
    \right\} I(z_l > 0) \\
        &\propto \exp \left\{ -\frac{ 1 }{ 2 } \left[ \Lambda_l {\tilde{z}_l}^2 - 2 \mu_l \tilde{z}_l \right] \right\}
\end{align*}
where
\begin{align*}
    \mu_l &= \lambda ( R_1^\prime \Omega_{11} + R_2^\prime \Omega_{21} )\bOne\\
    \Lambda_l &= \lambda^2 \bOne^\prime \Omega_{11} \bOne + \frac{ 1 }{ \sigma^2_l }.
\end{align*}
Then $\tilde{Z}_l | \ldots \sim N_{(0, \infty)} (\Lambda_l^{-1} \mu_l, \Lambda_l^{-1})$

\subsection*{Conditional posterior of $\beta \mid \ldots$}\label{sts:betapost}
Let $\beta \sim \mbox{N}_{p}(0, \Lambda_0)$ where $\Lambda_0$ is a precision matrix. Then
\begin{align*}
    \pi(\beta \mid \ldots) & \propto \exp \left\{ - \frac{ 1 }{ 2 } \beta^\prime \Lambda_0 \beta - \frac{ 1 }{ 2 } \sum_{t = 1}^{n_t} [\bY_t - X_t \beta - \lambda |z_t|]^\prime \Omega [\bY_t - X_t \beta - \lambda |z_t|] \right\}\\
     & \propto \exp \left\{ -\frac{ 1 }{ 2 } \left[ \beta^\prime \Lambda_\beta \beta  - 2 \sum_{t = 1}^{n_t} [ \beta^\prime X_t^\prime \Omega (\bY_t - \lambda |z_t| )] \right] \right\}\\
     & \propto \mbox{N} ( \Lambda_\beta^{-1} \mu_\beta , \Lambda_\beta^{-1})
\end{align*}
where
\begin{align*}
    \mu_\beta &= \sum_{t = 1}^{n_t} \left[ X_t^\prime \Omega (\bY_t - \lambda |z_t|) \right]\\
    \Lambda_\beta &= \Lambda_0 + \sum_{t = 1}^{n_t} X_t^\prime \Omega X_t.
\end{align*}

\subsection*{Conditional posterior of $\sigma^2 \mid \ldots$}\label{sts:sigpost}
In the case where $L = 1$ and temporal dependence is negligible, then $\sigma^2$ has a conjugate posterior distribution.
Let $\sigma_t^2 \iid \mbox{IG}(\alpha_0, \beta_0)$. For simplicity, drop the subscript $t$. Then
\begin{align*}
    \pi(\sigma^2 \mid \ldots) & \propto (\sigma^2)^{ -\alpha_0 - 1 / 2 - n / 2 - 1} \exp \left\{ -\frac{\beta_0}{\sigma^2} - \frac{ |z|^2 }{2 \sigma^2} - \frac{ (\bY - \bmu)^\prime \Sigma^{-1} (\bY - \bmu) }{2 \sigma^2} \right\} \\
    & \propto (\sigma^2)^{ -\alpha_0 - 1 / 2 - n / 2 - 1} \exp \left\{ - \frac{ 1 }{ \sigma^2 } \left[\beta_0 + \frac{ |z|^2 }{ 2 } + \frac{ 1 }{ 2 } (\bY - \bmu)^\prime \Sigma^{-1} (\bY - \mu) \right] \right\} \\
    & \propto \mbox{IG} (\alpha^*, \beta^*)
\end{align*}
where
\begin{align*}
    \alpha^* &= \alpha_0 + \frac{1}{2} + \frac{n}{2} \\
    \beta^* &= \beta_0 + \frac{ |z|^2 }{ 2 } + \frac{ 1 }{ 2 }(\bY - \bmu)^\prime \Sigma^{-1} (\bY - \bmu).
\end{align*}
In the case that $L > 1$, a random walk Metropolis Hastings step will be used to update $\sigma^2_{lt}$.

\subsection*{Conditional posterior of $\lambda \mid \ldots$}\label{sts:lambdapost}
\hl{TODO: Still needs to be updated for single $\lambda$}\\
For convergence purposes we model $\lambda = \lambda_1 \lambda_2$ where
\begin{align}
  \lambda_1 &= \left\{ \begin{array}{ll}
      +1 \quad & \text{w.p.} 0.5\\
      -1 \quad & \text{w.p.} 0.5
   \end{array}\right.\\
   \lambda^2_2 & \sim IG(\alpha_\lambda, \beta_\lambda).\\
\end{align}
Then
\begin{align*}
  \pi(\lambda_2 \mid \ldots) &\propto {\lambda_2^2}^{(-\alpha_\lambda - 1)} \exp\left\{ - \frac{ \beta_\lambda }{ \lambda_2^2} \right\} \prod_{t = 1}^{n_t} \prod_{k = 1}^K \frac{1} {\lambda_2} \exp\left\{ - \frac{ z^2_{tk} }{ 2 \lambda_2^2  \sigma_{tk})^2} \right\} \\
   & \propto {\lambda_2^2}^{(-\alpha_\lambda - K*n_t - 1)} \exp \left\{ -\frac{1}{\lambda^2_2} \left[ \beta_\lambda + \frac{ z^2 }{2 \sigma^2_{tk}} \right] \right\}
\end{align*}
Then $\lambda_2 \mid \ldots \sim IG \left(\alpha_\lambda + K * n_t, \beta_\lambda + \frac{ z^2 }{2 \sigma^2_{tk}} \right)$

@@

\subsection*{Multivariate skew-$t$ distribution}
If $\bZ \sim \text{ST}_d(0, \bar{\bOmega}, \balpha, \eta)$ is a $d$-dimensional skew-$t$ distribution, and $\bY = \xi + \bomega \bZ$, where $\bomega = \text{diag}(\omega_1, \ldots, \omega_d)$, then the density of $Y$ at $y$ is
\begin{align}
  f_y(\by) = det(\bomega)^{-1} f_z(\bz)
\end{align}
where
\begin{align}
  f_z(\bz) &= 2 t_d(\bz; \bar{\bOmega}, \eta) T \left[ \balpha^\prime \bz \sqrt{ \frac{\eta + d}{\nu + Q(\bz)} }; \eta + d\right] \\
  \bz &= \bomega^{-1}(\by - \xi)
\end{align}
where $t_d(\bz; \bar{\bOmega}, \eta)$ is a $d$-dimensional Student's $t$-distribution with scale matrix $\bar{\bOmega}$ and degrees of freedom $\eta$, $Q(z) = \bz^\prime \bar{\Omega}^{-1}\bz$ and $T(\cdot; \eta)$ denotes the univariate Student's $t$ distribution function with $\eta$ degrees of freedom \citep{Azzalini2014}.

\subsection*{Extremal dependence}
For a bivariate skew-$t$ random variable $\bY = [Y(\bs), Y(\bt)]^\prime$, the $\chi(h)$ statistic \citep{Padoan2011} is given by
\begin{align} \label{steq:chiskew-t}
  \chi(h) = \bar{F}_{\text{EST}}\left\{ \frac{[x_1^{1 / \eta} - \varrho(h)] \sqrt{\eta + 1} }{\sqrt{1 - \varrho(h)^2}}; 0, 1, \alpha_1, \tau_1, \eta + 1 \right\} + \bar{F}_{\text{EST}}\left\{ \frac{ [x_2^{1 / \eta} - \varrho(h)] \sqrt{\eta + 1} }{ \sqrt{1 - \varrho(h)^2} }; 0, 1, \alpha_2, \tau_2, \eta + 1 \right\},
\end{align}
where $\bar{F}_{\text{EST}}$ is the univariate survival extended skew-$t$ function with zero location and unit scale, \hbox{$\varrho(h) = \text{cor}[y(\bs), y(\bt)]$}, $\alpha_j = \alpha_i \sqrt{1 - \varrho^2}$, $\tau_j = \sqrt{\eta + 1}(\alpha_j + \alpha_i \varrho)$, and $x_j = F_T(\bar{\alpha}_i \sqrt{\eta + 1}; 0, 1, \eta) / F_T(\bar{\alpha}_j \sqrt{\eta + 1}; 0, 1, \eta)$ with $j = 1, 2$ and $i = 2, 1$ and where $\bar{\alpha}_j = (\alpha_j + \alpha_i \varrho) / \sqrt{ 1 + \alpha_i^2 [1 - \varrho(h)^2]}$.

\subsection*{Proof that $\lim_{h \rightarrow \infty} \chi(h) > 0$}
Consider the bivariate distribution of $\bY = [Y(\bs), Y(\bt)]^\prime$, with $\varrho(h)$ given by \eref{steq:matern}.
So, $\lim_{h \rightarrow \infty} \varrho(h) = 0$.
Then
\begin{align}
  \lim_{h \rightarrow \infty} \chi(h) = \bar{F}_{\text{EST}}\left\{ \sqrt{\eta + 1}; 0, 1, \alpha_1, \tau_1, \eta + 1 \right\} + \bar{F}_{\text{EST}}\left\{ \sqrt{\eta + 1}; 0, 1, \alpha_2, \tau_2, \eta + 1 \right\}.
\end{align}
Because the extended skew-$t$ distribution is not bounded above, for all $\bar{F}_{\text{EST}}(x) = 1 - F_{\text{EST} (x)} > 0$ for all $x < \infty$.
Therefore, for a skew-$t$ distribution, $\lim_{h \rightarrow \infty} \chi(h) > 0$.

>>>>

\subsection*{Spatial knot locations}
For each day, we update the spatial knot locations, $\bw_1, \ldots, \bw_K$, using a Metropolis-Hastings block update.
Because the spatial domain is bounded, we generate candidate knots using the transformed knots $\bw^*_1, \ldots, \bw^*_K$ (see \sref{sts:temporal}) and a random walk bivariate Gaussian candidate distribution
\begin{align*}
	{\bw^*_k}^{(c)} \sim \text{N}({\bw^*_k}^{(r - 1)}, s^2 I_2)
\end{align*}
where ${\bw^*_k}^{(r - 1)}$ is the location for the transformed knot at MCMC iteration $r - 1$, $s$ is a tuning parameter, and $I_2$ is an identity matrix.
Let $\bY_t = [Y(\bs_1), \ldots, Y(\bs_n)]$ be the vector of observed responses at each site for day $t$.
After candidates have been generated for all $K$ knots, the acceptance ratio is
\begin{align*}
  R = \left\{ \frac{ l[ \bY_t | \bw_1^{(c)}, \ldots, \bw_K^{(c)}, \ldots] }{l[ \bY_t | \bw_1^{(r - 1)}, \ldots, \bw_K^{(r - 1)}, \ldots]} \right\} \times \left\{ \frac{ \prod_{k = 1}^{K}\phi(\bw_k^{(c)})}{ \prod_{k = 1}^{K}\phi(\bw_k^{(r - 1)})} \right\} \times \left\{ \frac{ \prod_{k = 1}^{K} p({\bw^*_k}^{(c)})}{ \prod_{k = 1}^{K} p({\bw^*_k}^{(r - 1)})}\right\}
\end{align*}
where $l$ is the likelihood given in \eref{steq:hier}, and $p(\cdot)$ is the prior either taken from the time series (see \sref{sts:temporal}) or assumed to be uniform over $\calD$.
The candidate knots are accepted with probability $\min\{R, 1\}$.

\subsection*{Spatial random effects}
If there is no temporal dependence amongst the observations, we use a Gibbs update for $z_{tk}$, and the posterior distribution is given in \aref{sta:posterior}.
If there is temporal dependence amongst the observations, then we update $z_{tk}$ using a Metropolis-Hastings update.
Because this model uses $|z_{tk}|$, we generate candidate random effects using the $z^*_{tk}$ (see \sref{sts:temporal}) and a random walk Gaussian candidate distribution
\begin{align*}
  {z^*_{tk}}^{(c)} \sim \text{N}({z^*_{tk}}^{(r - 1)}, s^2)
\end{align*}
where ${z^*_{tk}}^{(r-1)}$ is the value at MCMC iteration $r - 1$, and $s$ is a tuning parameter.
The acceptance ratio is
\begin{align*}
  R = \left\{ \frac{ l[\bY_t | z_{tk}^{(c)}, \ldots] }{ l[\bY_t | z_{tk}^{(r - 1)}]} \right\} \times \left\{ \frac{ p[ z_{tk}^{(c)} ] }{ p[ z_{tk}^{(r - 1)}]}\right\}
\end{align*}
where $p[\cdot]$ is the prior taken from the time series given in \sref{sts:temporal}.
The candidate is accepted with probability $\min\{R, 1\}$.

\subsection*{Variance terms}
When there is more than one site in a partition, then we update $\sigma^2_{tk}$ using a Metropolis-Hastings update.
First, we generate a candidate for $\sigma^2_{tk}$ using an IG$(a^*/s, b^*/s)$ candidate distribution in an independence Metropolis-Hastings update where $a^* = (n_{tk} + 1) / 2 + a$, $b^* = [\bY_{tk}^\top \Sigma^{-1}_{tk} \bY_{tk} + z_{tk}^2] / 2 + b$, $n_{tk}$ is the number of sites in partition $k$ on day $t$, and $\bY_{tk}$ and $\Sigma^{-1}_{tk}$ are the observations and precision matrix for partition $k$ on day $t$.
The acceptance ratio is
\begin{align*}
  R = \left\{
    \frac{ l[\bY_t | {\sigma^2_{tk}}^{(c)}, \ldots] }
         { l[\bY_t | {\sigma^2_{tk}}^{(r - 1)}]}
    \right\} \times \left\{
    \frac{ l[z_{tk} | {\sigma^2_{tk}}^{(c)}, \ldots] }
         { l[z_{tk} | {\sigma^2_{tk}}^{(r - 1)}, \ldots] }
    \right\} \times \left\{
    \frac{ p[ {\sigma^2_{tk}}^{(c)} ] }
         { p[ {\sigma^2_{tk}}^{(r - 1)}] }
    \right\} \times \left\{
    \frac{ c[ {\sigma^2_{tk}}^{(r - 1)}] }
         { c[ {\sigma^2_{tk}}^{(c)}]}
    \right\}
\end{align*}
where $p[\cdot]$ is the prior either taken from the time series given in \sref{sts:temporal} or assumed to be IG$(a, b)$, and $c[\cdot]$ is the candidate distribution.
The candidate is accepted with probability $\min\{R, 1\}$.

\subsection*{Spatial covariance parameters}
We update the three spatial covariance parameters, $\log(\rho)$, $\log(\nu)$, $\gamma$, using a Metropolis-Hastings block update step.
First, we generate a candidate using a random walk Gaussian candidate distribution
\begin{align*}
	\log(\rho)^{(c)} \sim \text{N}(\log(\rho)^{(r - 1)}, s^2)
\end{align*}
where $\log(\rho)^{(r-1)}$ is the value at MCMC iteration $r - 1$, and $s$ is a tuning parameter.
Candidates are generated for $\log(\nu)$ and $\gamma$ in a similar fashion.
The acceptance ratio is
\begin{align*}
	R = \left\{ \frac{ \prod_{t = 1}^{n_t} l[Y_t(\bs) | \rho^{(c)}, \nu^{(c)}, \gamma^{(c)}, \ldots] }{\prod_{t = 1}^{n_t} l[Y_t(\bs) | \rho^{(r-1)}, \nu^{(r-1)}, \gamma^{(r-1)}, \ldots] } \right\} \times \left\{ \frac{ p[\rho^{(c)}] }{ p[\rho^{(r - 1)] } } \right\} \times \left\{ \frac{ p[\nu^{(c)}] }{ p[\nu^{(r - 1)}] } \right\} \times \left\{ \frac{ p[ \gamma^{(c)} ] }{ p[\gamma^{(r - 1)} ] } \right\}.
\end{align*}
All three candidates are accepted with probability $\min\{R, 1\}$.

@@

\subsection*{Conditional posterior of $z_{tk} \mid \ldots $}\label{sts:mvcondu}
If knots are independent over days, then the conditional posterior distribution of $|z_{tk}|$ is conjugate.
For simplicity, drop the subscript $t$, let $\tilde{z}_{k} = |z_{k}|$, $\tilde{\bz}_{k^c}$ be the vector of $[|z(\bs_1)|, \ldots, |z(\bs_n)|]$ for $\bs \notin P_k$, $\bX = [\bX(\bs_1), \ldots, \bX(\bs_n)]^\top$, let $\bY_k$ and $\bX_k$ be the observations and covariate measurements for $\bs \in P_k$, and let $\bY_{k^c}$ and $\bX_{k^c}$ be the observations and covariate measurements for $\bs \notin P_k$ and define
\begin{align*}
\bR = \left\{
    \begin{array}{ll}
        \bY_k - \bX_k \bbeta & \bs \in P_k\\[1em]
        \bY_{k^c} - \bX_{k^c} \bbeta - \lambda \tilde{\bz}_{k^c} \qquad & \bs \notin P_k
    \end{array}
\right.
\end{align*}
Let
\begin{align*}
    \bR_1 &= \text{the vector of } \bR \text{ for } \bs \in P_k \\
    \bR_2 &= \text{the vector of } \bR \text{ for } \bs \notin P_k \\
    \Omega &= \Sigma^{-1}.
\end{align*}
Then
\begin{align*}
    \pi(z_k | \ldots) &\propto \exp \left\{ -\frac{ 1 }{ 2 } \left[
        \left( \begin{array}{c}
            \bR_1 - \lambda \tilde{z}_k \bOne\\
            \bR_2
        \end{array} \right)^\top
        \left( \begin{array}{cc}
            \Omega_{11} & \Omega_{12}\\
            \Omega_{21} & \Omega_{22}
        \end{array} \right)
        \left( \begin{array}{c}
            \bR_1 - \lambda \tilde{z}_k \bOne\\
            \bR_2
        \end{array} \right)
        +  \frac{ {\tilde{z}_k}^2 }{ \sigma_k^2 }\right]
    \right\} I(z_k > 0) \\
        &\propto \exp \left\{ -\frac{ 1 }{ 2 } \left[ \Lambda_k {\tilde{z}_k}^2 - 2 \mu_k \tilde{z}_k \right] \right\}
\end{align*}
where
\begin{align*}
    \mu_k &= \lambda ( \bR_1^\top \Omega_{11} + \bR_2^\top \Omega_{21} )\bOne\\
    \Lambda_k &= \lambda^2 \bOne^\top \Omega_{11} \bOne + \frac{ 1 }{ \sigma^2_k }.
\end{align*}
Then $\tilde{z}_k | \ldots \sim N_{(0, \infty)} (\Lambda_k^{-1} \mu_k, \Lambda_k^{-1})$

\subsection*{Conditional posterior of $\bbeta, \lambda \mid \ldots$}\label{sts:betapost}
For models that do not include a skewness parameter, we update $\bbeta$ as follows.
Let $\bbeta \sim \mbox{N}_{p}(0, \Lambda_0)$ where $\Lambda_0$ is a precision matrix.
Then
\begin{align*}
    \pi(\bbeta \mid \ldots) & \propto \exp \left\{ - \frac{ 1 }{ 2 } \bbeta^\top \Lambda_0 \bbeta - \frac{ 1 }{ 2 } \sum_{t = 1}^{n_t} [\bY_t -\bX_t \bbeta]^\top \Omega [\bY_t - \bX_t \bbeta] \right\} \\
     & \propto \exp \left\{ -\frac{ 1 }{ 2 } \left[ \bbeta^\top \Lambda_\beta \bbeta  - 2 \sum_{t = 1}^{n_t} (\bbeta^\top \bX_t^\top \Omega \bY_t) \right] \right\} \\
     & \propto \mbox{N} ( \Lambda_\beta^{-1} \mu_\beta , \Lambda_\beta^{-1})
\end{align*}
where
\begin{align*}
    \mu_\beta &= \sum_{t = 1}^{n_t} \bX_t^\top \Omega \bY_t \\
    \Lambda_\beta &= \Lambda_0 + \sum_{t = 1}^{n_t} \bX_t^\top \Omega \bX_t.
\end{align*}
For models that do include a skewness parameter, a simple augmentation of the covariate matrix $\bX$ and parameter vector $\bbeta$ allows for a block update of both $\bbeta$ and $\lambda$.
Let $\bX^*_{t} = [\bX_t, |\bz_{t}|]$ where $\bz_t = [z(\bs_1), \ldots, z(\bs_{n})]^\top$ and let $\bbeta^* = (\beta_1, \ldots, \beta_p, \lambda)^\top$.
So to incorporate the $N(0, \sigma^2_\lambda)$ prior on $\lambda$, let $\bbeta^* \sim \mbox{N}_{p+1}(0, \Lambda^*_0)$ where
\begin{align*}
  \Lambda^*_0 = \left( \begin{array}{cc}
    \Lambda_0 & 0 \\
    0         & \sigma^{-2}_\lambda
  \end{array}\right).
\end{align*}
Then the update for both $\bbeta$ and $\lambda$ is done using the conjugate prior given above with $\bX_t = \bX_t^*$ and $\bbeta = \bbeta^*$

\subsection*{Conditional posterior of $\sigma^2 \mid \ldots$}\label{sts:sigpost}
In the case where $L = 1$ and temporal dependence is negligible, then $\sigma^2$ has a conjugate posterior distribution.
Let $\sigma_t^2 \iid \mbox{IG}(\alpha_0 / 2, \beta_0 / 2)$. For simplicity, drop the subscript $t$. Then
\begin{align*}
    \pi(\sigma^2 \mid \ldots) & \propto (\sigma^2)^{ -\alpha_0 / 2 - 1 / 2 - n / 2 - 1} \exp \left\{ -\frac{\beta_0}{2\sigma^2} - \frac{ |z|^2 }{2 \sigma^2} - \frac{ (\bY - \bmu)^\top \Sigma^{-1} (\bY - \bmu) }{2 \sigma^2} \right\} \\
    & \propto (\sigma^2)^{ -(\alpha_0 - 1 - n) / 2 - 1} \exp \left\{ - \frac{ 1 }{ 2 \sigma^2 } \left[\beta_0 + |z|^2 + (\bY - \bmu)^\top \Sigma^{-1} (\bY - \bmu) \right] \right\} \\
    & \propto \mbox{IG} (\alpha^*, \beta^*)
\end{align*}
where
\begin{align*}
    \alpha^* &= \frac{\alpha_0 + 1 + n}{2} \\
    \beta^* &= \frac{1}{2} \left[ \beta_0 + |z|^2 + (\bY - \bmu)^\top \Sigma^{-1} (\bY - \bmu) \right].
\end{align*}
In the case that $K > 1$, a random walk Metropolis Hastings step will be used to update $\sigma^2_{kt}$.

@@

\subsection*{Multivariate skew-$t$ distribution}
If $\bZ \sim \text{ST}_d(0, \bar{\bOmega}, \balpha, \eta)$ is a $d$-dimensional skew-$t$ distribution, and $\bY = \xi + \bomega \bZ$, where $\bomega = \text{diag}(\omega_1, \ldots, \omega_d)$, then the density of $Y$ at $y$ is
\begin{align}
  f_y(\by) = det(\bomega)^{-1} f_z(\bz)
\end{align}
where
\begin{align}
  f_z(\bz) &= 2 t_d(\bz; \bar{\bOmega}, \eta) T \left[ \balpha^\top \bz \sqrt{ \frac{\eta + d}{\nu + Q(\bz)} }; \eta + d\right] \\
  \bz &= \bomega^{-1}(\by - \xi)
\end{align}
where $t_d(\bz; \bar{\bOmega}, \eta)$ is a $d$-dimensional Student's $t$-distribution with scale matrix $\bar{\bOmega}$ and degrees of freedom $\eta$, $Q(z) = \bz^\top \bar{\Omega}^{-1}\bz$ and $T(\cdot; \eta)$ denotes the univariate Student's $t$ distribution function with $\eta$ degrees of freedom \citep{Azzalini2014}.

\subsection*{Extremal dependence}
For a bivariate skew-$t$ random variable $\bY = [Y(\bs), Y(\bt)]^\top$, the $\chi(h)$ statistic \citep{Padoan2011} is given by
\begin{align} \label{steq:chiskew-t}
  \chi(h) = \bar{F}_{\text{EST}}\left\{ \frac{[x_1^{1 / \eta} - \varrho(h)] \sqrt{\eta + 1} }{\sqrt{1 - \varrho(h)^2}}; 0, 1, \alpha_1, \tau_1, \eta + 1 \right\} + \bar{F}_{\text{EST}}\left\{ \frac{ [x_2^{1 / \eta} - \varrho(h)] \sqrt{\eta + 1} }{ \sqrt{1 - \varrho(h)^2} }; 0, 1, \alpha_2, \tau_2, \eta + 1 \right\},
\end{align}
where $\bar{F}_{\text{EST}}$ is the univariate survival extended skew-$t$ function with zero location and unit scale, \hbox{$\varrho(h) = \text{cor}[y(\bs), y(\bt)]$}, $\alpha_j = \alpha_i \sqrt{1 - \varrho^2}$, $\tau_j = \sqrt{\eta + 1}(\alpha_j + \alpha_i \varrho)$, and $x_j = F_T(\bar{\alpha}_i \sqrt{\eta + 1}; 0, 1, \eta) / F_T(\bar{\alpha}_j \sqrt{\eta + 1}; 0, 1, \eta)$ with $j = 1, 2$ and $i = 2, 1$ and where $\bar{\alpha}_j = (\alpha_j + \alpha_i \varrho) / \sqrt{ 1 + \alpha_i^2 [1 - \varrho(h)^2]}$.

\subsection*{Proof that $\lim_{h \rightarrow \infty} \chi(h) > 0$}
Consider the bivariate distribution of $\bY = [Y(\bs), Y(\bt)]^\top$, with $\varrho(h)$ given by \eref{steq:matern}.
So, $\lim_{h \rightarrow \infty} \varrho(h) = 0$.
Then
\begin{align}
  \lim_{h \rightarrow \infty} \chi(h) = \bar{F}_{\text{EST}}\left\{ \sqrt{\eta + 1}; 0, 1, \alpha_1, \tau_1, \eta + 1 \right\} + \bar{F}_{\text{EST}}\left\{ \sqrt{\eta + 1}; 0, 1, \alpha_2, \tau_2, \eta + 1 \right\}.
\end{align}
Because the extended skew-$t$ distribution is not bounded above, for all $\bar{F}_{\text{EST}}(x) = 1 - F_{\text{EST} (x)} > 0$ for all $x < \infty$.
Therefore, for a skew-$t$ distribution, $\lim_{h \rightarrow \infty} \chi(h) > 0$.
